A Mechanical Formalization of Higher-Ranked Polymorphic Type Inference

### 2019-03-01 sections/Related.tex
S6 RW let arguments go first

>>>>

\jimmy{Let arguments go first by Ningning}
In a more recent work, \citet{xie2018letarguments} proposed a variant of
bidirectional type inference system where type information flows from arguments to
functions with an additional \emph{application} mode,
which allows more higher-order typed programs to be inferred without additional annotations.
Following the new mode, the let-generalization of the Hindley-Milner system
is well supported as a syntactic sugar.
Unfortunately, no formal proofs are given for the correctness of its algorithmic system.
